---
title: "Exposure Doesn't Pay the Bills:"
subtitle: .small[Aristic Production under Algorithmic Uncertainty in Streaming Markets]
author: "Aaron Graybill"
date: "05 April 2022"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    includes:
      in_header:
    css: [xaringan-themer.css, bullets.css]
biblio-style: apalike
csl: ../Inputs/apa.csl
bibliography: ../Inputs/RunningBib.bib
---
```{r setup, include=FALSE}
options(htmltools.dir.version = T)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
library(ggplot2)
style_duo_accent(
  primary_color = "#8C2730",
  secondary_color= "#D8E6F2",
  black_color = "#13091C",
  title_slide_background_image = "image (3).jpg",
  #title_slide_background_size = "contain",
  header_font_google = google_font("Playfair Display"),
  text_font_google   = google_font("Average", "300", "300i"),
  code_font_google   = google_font("Fira Mono"),
  text_font_size = "1.5rem",
  footnote_position_bottom = "10px"
  
)
```


# Outline

1.    Intro and Motivation
1.    Model
1.    Findings
1.    Questions
---
class: left

# Intro and Motivation
-   YouTube's 2021 Q3 Ad Revenue is $7.2B<sup>1</sup> 
-   Streaming Platforms are driven by **content creators**
-   Content creation can be a full time job
-   Creators make content, but algorithm decides who sees it

.footnote[
[1] [Source](https://abc.xyz/investor/static/pdf/2021Q3_alphabet_earnings_release.pdf)
]

---
# Motivation, continued. My Niche in the Literature

-   Artist's problem on streaming platforms
  - Choose ideal quantity and quality each period
-   Role of algorithmic uncertainty on producers
-   Effect of time on quality



---
class: center, middle
background-image: url("image (3).jpg")

# .white[The Model]

---

## What should a model describe?

.lesspaced[
### Consumer Behavior:
-   Artist discovery
-   Consumption based on quality

### Artist/Content Creator:
-   Maximize royalties from streams
-   Quality-quantity trade-off under audience uncertainty

### Streaming Platform:
- Algorithmic consumer-artist matching
- Useful but imperfect matching 
]

---

# Putting the pieces together

### Audience Evolution
#### $\mathcal{A}(m,n,A,\varepsilon)$

### Consumer demand
#### $\nu(z)$

---

# Putting the pieces together:

### Per-period revenue: 
#### $\mathcal{A}(m,n,A,\varepsilon)\nu(z)r$

### Subject to:

#### $f(m,z)=\kappa$

---

## Insights from a binary-choice one period model

- There is a strategy cutoff dependent on $A$:
  - Established artists choose high quality, new artists choose more exposure
- If algorithm is very favorable to new artists, both may choose high quality
- *This doesn't rely on functional form assumptions*

---

class: center, middle, inverse
background-image: url("image (3).jpg")

</br>
</br>
# .white[Dynamic Problem and Main Results]

---
## Solving Dynamically Using Recursion:

\begin{gather*}
V(n_{-1},A_{-1})=\max_{m,z}\left\{E[Anr+\rho V(n,A)]\right\} \\
s.t. \\
A=\mathcal{A}(m,n_{-1},A_{-1},\varepsilon), \ \text{Audience Evolution} \\
n=\nu(z), \ \text{Consumer Demand}  \\
f(m,z)=\kappa, \ \text{Tradeoff}
\end{gather*}

---

## Solving for $V$ and optimal $m,z$:

\begin{gather*}
V(n_{-1},A_{-1})=\max_{m,z}\left\{E[Anr+\rho V(n,A)]\right\}
\end{gather*}

- In this form, we have preexisting solving techniques!
- Solutions computed numerically
- Calibrated baseline for boundedness, interior solutions
  - Should not interpret magnitude of numbers, only differences from baseline
---

## Three variations from the baseline:

```{r,echo=F,warning=F,message=F,fig.asp = 1/1.8, fig.align = 'center', echo = FALSE, out.width = "110%", dpi= 300, warning = FALSE,message=FALSE}
library(dplyr)
d30 <- 
  read.csv("../VFI_Data/SimulationData/sim_d30.csv")
k20 <- 
  read.csv("../VFI_Data/SimulationData/sim_k20.csv")
k10 <- 
  read.csv("../VFI_Data/SimulationData/sim_k10.csv")
sd5 <- 
  read.csv("../VFI_Data/SimulationData/sim_sd5.csv")


d30 <- 
  d30 %>% 
  mutate(sim="d30") %>% 
  rename(m=1, v =2, A =3, n =4, u=5, t=6, ids=7)
k20 <- 
  k20 %>% 
  mutate(sim="k20") %>% 
  rename(m=1, v =2, A =3, n =4, u=5, t=6, ids=7)
k10 <- 
  k10 %>% 
  mutate(sim="k10") %>% 
  rename(m=1, v =2, A =3, n =4, u=5, t=6, ids=7)
sd5 <- 
  sd5 %>% 
  mutate(sim="sd5") %>% 
  rename(m=1, v =2, A =3, n =4, u=5, t=6, ids=7)

d <- 
  d30 %>% 
  full_join(k20) %>% 
  full_join(k10) %>% 
  full_join(sd5) %>% 
  mutate(z=case_when(sim=="k10"~10/m,
                     T~20/m))

d <- 
  d %>% 
  filter(ids<100) %>% 
  filter(t!=0 & t!=99)

d_roll <- 
  d %>% 
  select(sim,t,A,ids) %>% 
  group_by(sim,t) %>% 
  summarize(A=mean(A))

  

p_z <- 
  ggplot(d) +
  geom_line(aes(x=t,y=z,group=interaction(ids,sim),col=sim),alpha=.1)+
  guides(colour = guide_legend(override.aes = list(alpha = 1,size=5)))+
  xaringanthemer::theme_xaringan(text_font_size=13,title_font_size = 13)+
  ylab("Quality")+
  xlab("Time")+
  scale_color_manual(values = c("#8C2730","#F28D9F","#255059","#FFBA3D"),labels=c("High Loyalty", "Low Talent", "Baseline", "High Volatility"),name=element_blank())

p_A <- 
  ggplot(d) +
  geom_line(aes(x=t,y=A,group=interaction(ids,sim),col=sim),alpha=.1)+
  geom_line(data=d_roll,aes(x=t,y=A,col=sim))+
  scale_color_manual(values = c("#8C2730","#F28D9F","#255059","#FFBA3D"),labels=c("High Loyalty", "Low Talent", "Baseline", "High Volatility"),name=element_blank())+
  scale_y_continuous(position = "right")+
  ylab("Audience")+
  xlab("Time")+
  xaringanthemer::theme_xaringan(text_font_size=13,title_font_size = 13)

ggpubr::ggarrange(p_z,p_A, ncol=2, nrow=1, common.legend = TRUE, legend="bottom")
```

---
## Conclusion
.lesspaced[
- Quality does not determine audience
]
.lesspaced[
- Successful artists shift from lower to higher quality
  - After they "go viral"
]
.lesspaced[
- Agents who do not understand the algorithm will not maintain audience
]
.lesspaced[
- Talent can also filter out artists
]
.lesspaced[
- Future research: 
  - How does talent influence distribution of revenue
  - Fit with data
]

---
class: center, middle
background-image: url("image (3).jpg")

</br>
</br>
# .white[Thanks, Questions?]

---

```{r, load_refs, echo=FALSE,message=F}
library(RefManageR)
bib <- ReadBib("../RunningBib.bib", check = FALSE)
#ui <- "- "
```
.tiny[
```{r, print_refs, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
#writeLines(ui)?
print(bib[key = c("aguiarQualityPredictabilityWelfare2018","kleinRoleMarketForces1981","shapiroPremiumsHighQuality1983","thomesEconomicAnalysisOnline2013","macdonaldEconomicsRisingStars1988","shapiroPremiumsHighQuality1983")], 
  .opts = list(check.entries = FALSE, 
               style = "html", 
               bib.style = "authoryear"))
```
]
---


## Visualizing Audience Uncertainty:

```{r Audience Uncertanity, fig.asp = 1, fig.align = 'center', echo = FALSE, out.width = "65%", dpi= 300, warning = FALSE,message=FALSE}
library(extrafont)
m=seq(0,10,.001)
A_0=4
I_up=.75*A_0+m+m*1.1
I_down=.75*A_0+m-m*1.1
I_mid=.75*A_0+m

q <- 
  tibble::tibble(m,I_up,I_down,I_mid)

library(ggplot2)
library(latex2exp)
ggplot(q)+
  geom_line(aes(m,I_mid,color="Expected Audience"),size=1.1)+
  theme(axis.text.y = element_text(angle = 45))+
  geom_ribbon(aes(m,ymin=I_down,ymax=I_up,color="Range of Audience"),alpha=.2,fill="#211030")+
  theme_bw()+
  annotate("text", x = 0.5, y = 1, label = "(1-δ)A",family="sans",size=7)+
  ylab(TeX("\nAudience at time $t$, $A$"))+
  xlab(TeX("Number of Releases, $m$"))+
  xlim(0,10)+
  ylim(0,25)+
  scale_color_manual(values=c("#8C2730","#211030"))+
  theme(legend.title=element_blank())+
  # scale_y_continuous(breaks = c(3),
  #                    labels = c(TeX("$(1-\\delta)A_{t-1}$")))+
  # scale_x_continuous(breaks = c(0),
  #                    labels = c(0))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"))+
  theme(legend.position="bottom")+
    theme(axis.text.x=element_blank(), #remove x axis labels
        axis.ticks.x=element_blank(), #remove x axis ticks
        axis.text.y=element_blank(),  #remove y axis labels
        axis.ticks.y=element_blank()  #remove y axis ticks
        )+
  xaringanthemer::theme_xaringan(text_font_size=17,title_font_size = 17)
```
 
---


## Functional Forms
.small[
\begin{gather}
\mathcal{A}(m,n,A,\varepsilon)=\frac{\overline{A}}{1+ce^{-\alpha n-\beta m-\gamma\varepsilon}}, c=\frac{\overline{A}-(1-\delta)A}{(1-\delta)A}\\
f(m,z)=mz\\
n(z)=\overline{n}(1-e^{-\lambda z})\\
\varepsilon \sim N(0,\sigma^2)
\end{gather}
]

---


```{r, fig.asp = 3/4, fig.align = 'center', echo = FALSE, out.width = "110%", dpi= 300, warning = FALSE,message=FALSE}
v=read.csv("../VFI_Data/v.csv",header=F)
m=read.csv("../VFI_Data/m.csv",header=F)
nn=read.csv("../VFI_Data/nn.csv",header=F)
AA=read.csv("../VFI_Data/AA.csv",header=F)

m <- as.matrix(m)
m <- c(m)

v <- as.matrix(v)
v <- c(v)

nn <- as.matrix(nn)
nn <- c(nn)

AA <- as.matrix(AA)
AA <- c(AA)

d <- 
  data.frame(v=v,m=m,nn=nn,AA=AA)

library(ggplot2)

ggplot(d %>% filter(m>.5)) +
  geom_point(aes(x = AA, y = m, col = nn)) +
  ylab(TeX("Optimal Quantity of Releases, $m$")) +
  xlab(TeX("Initial Audience Size, $A$")) +
  scale_color_gradient(low = "#211030", high = "#FFBA3D",name="Initial Streams\nPer Capita, n") +
  theme(text = element_text(family = "Tahoma")) +
  theme(legend.title = element_text(hjust = .5)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black"),
    #axis.ticks = element_blank(),
    #axis.text = element_blank()
    #legend.position = "bottom"
  )+
  xaringanthemer::theme_xaringan(text_font_size=17,title_font_size = 17)


# TWO cases of kappa
# show the 

```

---


```{r, fig.asp = 3/4, fig.align = 'center', echo = FALSE, out.width = "110%", dpi= 300, warning = FALSE,message=FALSE}
library(ggplot2)
library(extrafont)


ggplot(d) +
  geom_point(aes(x = AA, y = v, col = nn)) +
  ylab(TeX("Expected Discounted Lifetime Optimized Revenue, $V(n,A)$")) +
  xlab(TeX("Initial Audience Size, $A$")) +
  scale_color_gradient(low = "#211030", high = "#FFBA3D",name="Initial Streams\nPer Capita, n") +
  theme(text = element_text(family = "Tahoma")) +
  theme(legend.title = element_text(hjust = .5)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black"),
    #axis.ticks = element_blank(),
    #axis.text = element_blank()
    #legend.position = "bottom"
  )+
  xaringanthemer::theme_xaringan(text_font_size=17,title_font_size = 17)
```
---


```{r plot of n,fig.align = 'center', echo = FALSE, out.width = "110%", dpi= 300, warning = FALSE,message=FALSE,fig.asp = 3/4, fig.align = 'center',}
library(extrafont)
z=seq(0,12,.001)
n=5*(1-exp(-z))

q <- 
  tibble::tibble(z,n)

library(ggplot2)
library(latex2exp)
ggplot(q)+
  geom_line(aes(z,n),size=1.1,color="#211030")+
  xaringanthemer::theme_xaringan(text_font_size=17,title_font_size = 17)+
  scale_color_manual(values=c("#255059","#8C2730","#FFBA3D","#F28D9F"),name="Case")+
  geom_vline(aes(xintercept=10,color="High Loyalty"))+
  geom_vline(aes(xintercept=7.5,color="High Volatility"))+
  geom_vline(aes(xintercept=4,color="Low Talent"))+
  geom_vline(aes(xintercept=1,color="Baseline"))+
  ylab("Streams Per Capita")+
  xlab("Quality")
  


#   annotate("text", x = 0.5, y = 1, label = "(1-δ)A",family="sans",size=7)+
#   ylab(TeX("\nAudience at time $t$, $A$"))+
#   xlab(TeX("Number of Releases, $m$"))+
#   xlim(0,10)+
#   ylim(0,25)+
#   scale_color_manual(values=c("#8C2730","#211030"))+
#   theme(legend.title=element_blank())+
#   # scale_y_continuous(breaks = c(3),
#   #                    labels = c(TeX("$(1-\\delta)A_{t-1}$")))+
#   # scale_x_continuous(breaks = c(0),
#   #                    labels = c(0))+
#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
# panel.background = element_blank(), axis.line = element_line(colour = "black"))+
#   theme(legend.position="bottom")+
#     theme(axis.text.x=element_blank(), #remove x axis labels
#         axis.ticks.x=element_blank(), #remove x axis ticks
#         axis.text.y=element_blank(),  #remove y axis labels
#         axis.ticks.y=element_blank()  #remove y axis ticks
#         )+
#   xaringanthemer::theme_xaringan(text_font_size=17,title_font_size = 17)
```

---


```{r, fig.asp = 3/4, fig.align = 'center', echo = FALSE, out.width = "110%", dpi= 300, warning = FALSE,message=FALSE}
library(dplyr)
d_10 <- 
  d %>% 
  mutate(k="10")

v=read.csv("../VFI_Data/v_k15.csv",header=F)
m=read.csv("../VFI_Data/m_k15.csv",header=F)
nn=read.csv("../VFI_Data/nn_k15.csv",header=F)
AA=read.csv("../VFI_Data/AA_k15.csv",header=F)

m <- as.matrix(m)
m <- c(m)

v <- as.matrix(v)
v <- c(v)

nn <- as.matrix(nn)
nn <- c(nn)

AA <- as.matrix(AA)
AA <- c(AA)

d_15 <- 
  data_frame(v=v,m=m,nn=nn,AA=AA) %>% 
  mutate(k="15")

v=read.csv("../VFI_Data/v_k5.csv",header=F)
m=read.csv("../VFI_Data/m_k5.csv",header=F)
nn=read.csv("../VFI_Data/nn_k5.csv",header=F)
AA=read.csv("../VFI_Data/AA_k5.csv",header=F)

m <- as.matrix(m)
m <- c(m)

v <- as.matrix(v)
v <- c(v)

nn <- as.matrix(nn)
nn <- c(nn)

AA <- as.matrix(AA)
AA <- c(AA)

d_5 <- 
  data_frame(v=v,m=m,nn=nn,AA=AA) %>% 
  mutate(k="5")

library(tidyr)
d_k <- 
  full_join(d_15,d_10) %>% 
  full_join(d_5)# %>% 
  #pivot_longer(cols=c(m,v))

d_k$k <- factor(d_k$k, levels = c("5", "10", "15"))
d_k <- 
  d_k %>% 
  mutate(z=as.numeric(as.character(k))/m)

# ggplot(d_k %>% 
#          filter(m > .5)) +
#   geom_point(aes(
#     x = AA,
#     y = m,
#     col = nn,
#     shape = k
#   )) +
#   ylab(TeX("Optimal Quantity, $m$")) +
#   xlab(TeX("Initial Audience Size, $A$")) +
#   scale_color_gradient(low = "#211030", high = "#FFBA3D", name = "Initial Streams\nPer Capita, n") +
#   scale_shape(name=TeX("Talent, $\\kappa$"))+
#   theme(text = element_text(family = "Tahoma")) +
#   theme(legend.title = element_text(hjust = .5)) +
#   theme(
#     panel.grid.major = element_blank(),
#     panel.grid.minor = element_blank(),
#     panel.background = element_blank(),
#     axis.line = element_line(colour = "black")
#   )+
  # guides(shape = guide_legend(override.aes = list(color = "#211030")))

m=seq(.5,10,.001)

z_up=15/m
z_mid=10/m
z_down=5/m

library(dplyr)

q <- 
  tibble::tibble(m,z_up,z_down,z_mid) %>%
  select(z_down,z_mid,z_up,m) %>% 
    rename(`High Talent`=z_up,
         `Middle Talent`=z_mid,
         `Low Talent`=z_down) %>% 
  tidyr::pivot_longer(cols=c(`High Talent`:`Low Talent`))


ggplot(q %>% filter(m<10 & value<10))+
  geom_line(aes(m,value,size=name,color=name))+
  ylim(0,10)+
  xlim(0,10)+
  ylab(TeX("\nAvailable Quality, $z$"))+
  xlab(TeX("Number of Releases, $m$"))+
  scale_color_manual(values=c("#8C2730","#211030","#255059"))+
  scale_size_manual(values=c(.5,1,1.5))+
  theme(text = element_text(family = "Tahoma")) +
  theme(legend.title=element_blank())+
  # scale_y_continuous(breaks = c(3),
  #                    labels = c(TeX("$(1-\\delta)A_{t-1}$")))+
  # scale_x_continuous(breaks = c(0),
  #                    labels = c(0))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"),
axis.ticks=element_blank(),
axis.text = element_blank())+
  geom_point(data=d_k,aes(x=m,y=z),color="#FFBA3D",alpha=.5,shape=0)+
  xaringanthemer::theme_xaringan(text_font_size=17,title_font_size = 17)
```

---


```{r, fig.asp = 3/4, fig.align = 'center', echo = FALSE, out.width = "110%", dpi= 300, warning = FALSE,message=FALSE}
d_10 <- 
  d %>% 
  mutate(g="0.10")

v=read.csv("../VFI_Data/v_g15.csv",header=F)
m=read.csv("../VFI_Data/m_g15.csv",header=F)
nn=read.csv("../VFI_Data/nn.csv",header=F)
AA=read.csv("../VFI_Data/AA.csv",header=F)

AA <- as.matrix(AA)
AA <- c(AA)

nn <- as.matrix(nn)
nn <- c(nn)


m <- as.matrix(m)
m <- c(m)

v <- as.matrix(v)
v <- c(v)

d_one <- 
  data_frame(v=v,m=m,nn=nn,AA=AA) %>% 
  mutate(g="1.0")

v=read.csv("../VFI_Data/v_g0.csv",header=F)
m=read.csv("../VFI_Data/m_g0.csv",header=F)

m <- as.matrix(m)
m <- c(m)

v <- as.matrix(v)
v <- c(v)

d_0 <- 
  data_frame(v=v,m=m,nn=nn,AA=AA) %>% 
  mutate(g="0.0")

v=read.csv("../VFI_Data/v_gten.csv",header=F)
m=read.csv("../VFI_Data/m_gten.csv",header=F)

m <- as.matrix(m)
m <- c(m)

v <- as.matrix(v)
v <- c(v)

d_ten <- 
  data_frame(v=v,m=m,nn=nn,AA=AA) %>% 
  mutate(g="10")

d_g <- d_10 %>% 
  full_join(d_one) %>% 
  full_join(d_0) %>% 
  full_join(d_ten)# %>% 
  #pivot_longer(cols=c(m,v))

d_g_wide <- 
  d_g %>% 
  select(-m) %>% 
  pivot_wider(names_from = g,values_from = v) %>% 
  group_by(AA,nn) %>% 
  summarize(across(everything(),mean)) %>% 
  mutate(across(`1.0`:`10`,~(.x-`0.10`)/(`0.10`))) %>% 
  select(-`0.10`) %>% 
  pivot_longer(`1.0`:`10`,values_to = "v",names_to = "g")%>% 
  ungroup()

d_g_sum <- 
  d_g %>% 
  group_by(g,AA) %>% 
  summarize(across(v:nn,median)) %>% 
  mutate(g=as.character(g)) 

ggplot(d_g_wide %>% 
         filter(AA>min(AA))) +
  geom_point(aes(
    x = AA,
    y = v,
    shape = g,
    color = g
  )) +
  ylab(TeX("% Difference from Baseline Optimized Lifetime Utility, $V$")) +
  xlab(TeX("Initial Audience Size, $A$")) +
  #scale_color_gradient(low = "#211030", high = "#FFBA3D", name = "Initial Streams\nPer Capita, n") +
  scale_color_manual(values=c("#8C2730","#211030","#255059"),
                     name=TeX("Algorithmic Uncertainty, $\\gamma$"))+
  scale_shape(name=TeX("Algorithmic Uncertainty, $\\gamma$"))+
  theme(text = element_text(family = "Tahoma")) +
  theme(legend.title = element_text(hjust = .5)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black")
  )+
guides(shape = guide_legend(override.aes = list(color = "#211030")))+
  xaringanthemer::theme_xaringan(text_font_size=17,title_font_size = 17)
```

---


```{r, fig.asp =3/4, fig.align = 'center', echo = FALSE, out.width = "110%", dpi= 300, warning = FALSE,message=FALSE}
d_70 <- 
  d %>% 
  mutate(d="0.70")

v=read.csv("../VFI_Data/v_d85.csv",header=F)
m=read.csv("../VFI_Data/m_d85.csv",header=F)

m <- as.matrix(m)
m <- c(m)

v <- as.matrix(v)
v <- c(v)

d_85 <- 
  data_frame(v=v,m=m,nn=nn,AA=AA) %>% 
  mutate(d="0.85")

v=read.csv("../VFI_Data/v_d1.csv",header=F)
m=read.csv("../VFI_Data/m_d1.csv",header=F)

m <- as.matrix(m)
m <- c(m)

v <- as.matrix(v)
v <- c(v)

d_10 <- 
  data_frame(v=v,m=m,nn=nn,AA=AA) %>% 
  mutate(d="0.1")

d_d <- 
  full_join(d_10,d_70) %>% 
  full_join(d_85) %>% 
  full_join(d_10)
  #pivot_longer(cols=c(m,v))

d_d_sum <- 
  d_d %>% 
  group_by(d,AA) %>% 
  summarize(across(v:nn,median))


ggplot(d_d_sum %>%
         filter(m > .5)) +
  geom_point(aes(
    x = AA,
    y = 10 / m,
    col = d,
    #col = nn,
    shape = d,
    group = d
  ), alpha = 1) +
    geom_line(aes(
    x = AA,
    y = 10 / m,
    col = d), alpha = 1) +
  ylab(TeX("Median Optimal Quality, $z$")) +
  xlab(TeX("Initial Audience Size, $A$")) +
  scale_color_manual(
    name = TeX("Audience Depreciation, $\\delta$"),
    values = c("#8C2730", "#211030", "#255059"),
    labels =c("Low, .1","Baseline, .7", "High, .85")
  ) +
  scale_shape_manual(name = TeX("Audience Depreciation, $\\delta$"),
    labels =c("Low, .1","Baseline, .7", "High, .85"),
    values = c(0,1,2)) +
  theme(text = element_text(family = "Tahoma")) +
  theme(legend.title = element_text(hjust = .5)) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black")
  ) +
  guides(shape = guide_legend(override.aes = list(alpha = 1)))+
  xaringanthemer::theme_xaringan(text_font_size=17,title_font_size = 17)

```
