---
title: "Update Presentation, Curvy Conundrums"
#subtitle: "Aristic Production and Algorithmic Uncertainty in Streaming Markets"
author: "Aaron Graybill"
date: "π-Day 2022"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    includes:
      in_header:
    css: [xaringan-themer.css, bullets.css]
biblio-style: apalike
csl: ../Inputs/apa.csl
bibliography: ../RunningBib.bib
---
```{r setup, include=FALSE}
options(htmltools.dir.version = T)
knitr::opts_chunk$set(fig.width=10,fig.height = 6)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#8C2730",
  secondary_color= "#D8E6F2",
  black_color = "#13091C",
  title_slide_background_image = "image (3).jpg",
  #title_slide_background_size = "contain",
  header_font_google = google_font("Playfair Display"),
  text_font_google   = google_font("Average", "300", "300i"),
  code_font_google   = google_font("Fira Mono"),
  text_font_size = "1.5rem",
  footnote_position_bottom = "10px"
)
```


# Outline

1.    Review The Current Iteration of the Model
2.    Discuss where and how curvature can be implemented
3.    Suggested Functional Forms
4.    Value function iteration?


---
class: left
# Review The Current Iteration of the Model
The model as it stands forces linearity of aglorithmic shocks
$$V(m,z)=\max_{m,z}\left\{E\left[rA_tn(z)-C(m,z;\kappa)\right]  \ \textrm{s.t.} \ \\ A_t=(1-\delta)A_{t-1}+mI(n_{t-1})+\sum_{i=1}^m\varepsilon_{it}\right\}$$
---
class: left
# Proposed More Flexible Model for this application:

$$V(m,z)=\max_{m,z}\left\{E\left[rA_tn(z)\right]  \ \textrm{s.t.} \ \\ A_t=(1-\delta)A_{t-1}+I(n_{t-1},m,\varepsilon), \\ f(m,z)=\kappa\right\}$$

---
class: left
## Problems with that model

- We need a functional form for:
  - $n(z)$, streams per quality after exposure (choosing good units might help)
  - $I(n_{t-1},m,\varepsilon)$, impressions per past quality, units this period, and random shock
  - $f(m,z)$, the production/time constraint (Cobb-Douglas??)
  
---
class: left
## Upsides of that system

- We can collapse the expectation component to:
 - $E[I(n_{t-1},m,\varepsilon)|n_{t-1},m]$
 - Allows curvature on $\varepsilon$ but minimal influence elsewhere
- Good choices of functional forms should allow for Dynamic Programming

---
class: left
## Proposed Functional Forms
- $I(n_{t-1},m,\varepsilon)=\ln\left(n_{t-1}^{\alpha} m^{\beta}\varepsilon^{\gamma}\right)$ with $\ln(\varepsilon)\sim N(0,\sigma^2)$
  - Nice Consequence that $E(I)=\alpha\ln(n_{t-1})+\beta\ln(m)+0$
  - We could do a taylor approach 
- $n(z)=z$ or $n(z)=cz$ just give units of quality such that one quality means one more stream per exposure
- $f(m,z)=(m/\overline{m})^q(z/\overline{z})^{1-q}$ where those are some normalizing constants. Basically Cobb-Douglas.

---
class: left

# A nice result:

- Astonishingly, we can actually solve the one period model in closed form if we use those assumptions.
- The biggest problem is that if we set $n(z)=z$, then cobb-douglas on $f$ probably doesn't make sense
- But if we ignore that, does that mean we can recursively solve the multiperiod case?
  - Well no, this period's choice of $z$ and $m$ affect next period's $n_{t-1}$ and $A_t-1$ respectively
- But dynamic programming?



  