---
title: "Exposure Doesn't Pay the Bills"
#subtitle: "Aristic Production and Algorithmic Uncertainty in Streaming Markets"
author: "Aaron Graybill"
date: "09 December 2021"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    includes:
      in_header:
        - 'Test.html'
    css: [xaringan-themer.css, bullets.css]
biblio-style: apalike
csl: ../apa.csl
bibliography: ../RunningBib.bib
---
```{r setup, include=FALSE}
options(htmltools.dir.version = T)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#8C2730",
  secondary_color= "#D8E6F2",
  black_color = "#261201",
  title_slide_background_image = "image (3).jpg",
  #title_slide_background_size = "contain",
  header_font_google = google_font("Playfair Display"),
  text_font_google   = google_font("Average", "300", "300i"),
  code_font_google   = google_font("Fira Mono"),
  text_font_size = "1.5rem",
  footnote_position_bottom = "10px"
)
```


# Outline

1.    Intro and Motivation
1.    Related Literature
1.    Model
1.    Initial Findings
1.    Questions


---
class: left
# Intro and Motivation

-   YouTube's 2021 Q3 Ad Revenue is $7.2B<sup>1</sup> 
-   Streaming Platforms are driven by **content creators**
-   Content creation can be a full time job
-   We should explore the evolution of quality and popularity 
-   Creators make content, but algorithm decides who sees it
    
.footnote[
[1] [Source](https://abc.xyz/investor/static/pdf/2021Q3_alphabet_earnings_release.pdf)
]
---

# Related Literature

### Branding
-   Klein and Leffler (1981)
-   Shapiro (1983)

### Superstar
-   Rosen (1981)
-   Macdonald (1988)

---
# Related Literature, cont.

### Streaming
-   Thomes (2013)
-   Aguiar & Waldfogel (2018)

### My Niche
-   Artist's optimal behavior
-   Role of algorithmic uncertainty
-   Time component

---
class: center, middle
background-image: url("image (3).jpg")

# .white[The Model]


---

## What should a model describe?

.lesspaced[
### Consumer Behavior:
-   Artist discovery
-   Consumption based on quality

### Streaming Platform:
- Algorithmic consumer-artist matching
- Useful but imperfect matching 

### Artist/Content Creator:
-   Quality-quantity trade-off under audience uncertainty
-   Maximize royalties from streams
]

---

# Consumer behavior

- No ex-ante knowledge of an artist, require algorithmic exposure
- If consumer knows about an artist they consume based on quality, $n(z)$
- Consumer forgets about an artist with probability $\delta$ every period.
- All consumers the same

---

# Artist Behavior

- Artist decides a quality, $z$, and quantity, $m$ subject to cost
  - All releases same quality in one period
- Artist gets royalty $r$ for every stream
- Artist can't choose audience size directly
- More releases $\to$ more chances to go viral

---
# Algorithmic Behavior

- Can't measure quality directly, can use consumer streams
  - Use last period's streams, $n_{t-1}$
-   For every release by an artist, algorithm shows:
  - $I(n_{t-1})+\varepsilon_{it}$, iid mean zero

---
# Putting the pieces together:

### Total Audience size: 

#### $A_t(m)=(1-\delta)A_{t-1}+mI(n_{t-1})+\sum_{i=1}^m \varepsilon_{it}$

### Per-period revenue: 

#### $rA_t(m)n(z)-C(m,z;\kappa)$

---
# The Artist's problem: 
</br></br>
 
\begin{gather*}
\max_{m,z}\left\{E\left(A_t(m)n(z)-C(m,z;\kappa)\right) \\
 s.t. \\
A_t(m)=(1-\delta)A_{t-1}+mI(n_{t-1})+\sum_{i=1}^m \varepsilon_{it}\right\}
\end{gather*}
---
class: center, middle
background-image: url("image (3).jpg")

</br>
</br>
# Initial Findings & Next Steps

---
## A nice result from a binary choice case

$1$ piece at quality $\overline{z}$, or $2$ pieces at $\underline z$

$$
\begin{cases}
2, &  \frac{n(\overline z)}{n(\underline z)} < \left(1+\frac{I_0}{I_0+(1-\delta)A_0}\right)\\
1, &  \frac{n(\overline z)}{n(\underline z)} > \left(1+\frac{I_0}{I_0+(1-\delta)A_0}\right)
\end{cases}
$$
Established artists choose high quality, new artists choose more exposure

---
## Next Steps

- Solve this in the two-period case (then $\infty$-period)
- Further explore how $\kappa$ reveals itself in the distribution of successful artists

---
class: center, middle
background-image: url("image (3).jpg")

</br>
</br>
# Thanks, Questions?


---

```{r, load_refs, echo=FALSE,message=F}
library(RefManageR)
bib <- ReadBib("../RunningBib.bib", check = FALSE)
#ui <- "- "
```
.tiny[
```{r, print_refs, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
#writeLines(ui)?
print(bib[key = c("aguiarQualityPredictabilityWelfare2018","kleinRoleMarketForces1981","shapiroPremiumsHighQuality1983","thomesEconomicAnalysisOnline2013","macdonaldEconomicsRisingStars1988","shapiroPremiumsHighQuality1983")], 
  .opts = list(check.entries = FALSE, 
               style = "html", 
               bib.style = "authoryear"))


```
]